Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-10-18 manuscript_latex/manuscript.tex
Update duplicate labels.

\subsection{Invariance}\label{invariance}

@@

\subsubsection{Age of patients with lung
cancer}\label{age-of-patients-with-lung-cancer}

@@

\subsubsection{Penguin body mass}\label{penguin-body-mass}

@@

\subsubsection{Latitude in the Ames housing
dataset}\label{latitude-in-the-ames-housing-dataset}

@@

\subsection{Robustness against
outliers}\label{robustness-against-outliers}

@@

\subsubsection{Fuel efficiency in the Top Gear
dataset}\label{fuel-efficiency-in-the-top-gear-dataset}

@@

\subsubsection{Maximum arterial wall thickness in an ischemic stroke
dataset}\label{maximum-arterial-wall-thickness-in-an-ischemic-stroke-dataset}

@@

\subsection{Invariance}\label{invariance}

@@

\subsubsection{Age of patients with lung
cancer}\label{age-of-patients-with-lung-cancer}

@@

\subsubsection{Penguin body mass}\label{penguin-body-mass}

@@

\subsubsection{Latitude in the Ames housing
dataset}\label{latitude-in-the-ames-housing-dataset}

@@

\subsection{Robustness against
outliers}\label{robustness-against-outliers}

@@

\subsubsection{Fuel efficiency in the Top Gear
dataset}\label{fuel-efficiency-in-the-top-gear-dataset}

@@

\subsubsection{Maximum arterial wall thickness in an ischemic stroke
dataset}\label{maximum-arterial-wall-thickness-in-an-ischemic-stroke-dataset}

>>>>

\subsection{Invariance}\label{sec:invariance}

@@

\subsubsection{Age of patients with lung
cancer}\label{sec:age-of-patients-with-lung-cancer}

@@

\subsubsection{Penguin body mass}\label{sec:penguin-body-mass}

@@

\subsubsection{Latitude in the Ames housing
dataset}\label{sec:latitude-in-the-ames-housing-dataset}

@@

\subsection{Robustness against
outliers}\label{sec:robustness-against-outliers}

@@

\subsubsection{Fuel efficiency in the Top Gear
dataset}\label{sec:fuel-efficiency-in-the-top-gear-dataset}

@@

\subsubsection{Maximum arterial wall thickness in an ischemic stroke
dataset}\label{sec:maximum-arterial-wall-thickness-in-an-ischemic-stroke-dataset}

@@

\subsection{Invariance}\label{sec-app:invariance}

@@

\subsubsection{Age of patients with lung
cancer}\label{sec-app:age-of-patients-with-lung-cancer}

@@

\subsubsection{Penguin body mass}\label{sec-app:penguin-body-mass}

@@

\subsubsection{Latitude in the Ames housing
dataset}\label{sec-app:latitude-in-the-ames-housing-dataset}

@@

\subsection{Robustness against
outliers}\label{sec-app:robustness-against-outliers}

@@

\subsubsection{Fuel efficiency in the Top Gear
dataset}\label{sec-app:fuel-efficiency-in-the-top-gear-dataset}

@@

\subsubsection{Maximum arterial wall thickness in an ischemic stroke
dataset}\label{sec-app:maximum-arterial-wall-thickness-in-an-ischemic-stroke-dataset}
